dyngen: simulating developing single cells

### 2019-08-28 content.tex
update
Update content.tex

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/showcase_3.png} 
	\caption{Showcase of dyngen functionality. \textbf{TODO: change to pdf.} Remove B?} % TODO: update label
	\label{fig:dyngen}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/simplecyclic_edited} 
	\caption{Showcase of dyngen functionality. A time resolution of 0.1 was used, but this can be increased or decreased without effect on performance of the execution of the simulation. \textbf{TODO: perhaps it's better to replace Figure \ref{fig:simplecyclic} with one subfigure for each of the paragraphs in this text.}}
	\label{fig:simplecyclic}
\end{figure}

@@

\section{Discussion}
As is, dyngen's single cell simulations can be used to evaluate common single-cell omics computational methods such as clustering, batch correction, trajectory inference and network inference.
However, the combined effect of these advantages results in a framework that is flexible enough to adapt to a broad range of applications; several examples are given.

@@

Currently, dyngen focuses on simulating cells as standalone entities.
Future developments include extending the framework to simulate multiple cells in a virtual environment. Allowing cells to receive and react to environmental and intercellular stimuli would enable simulating essential cellular processes such as cell division and migration.

\section{Methods}

>>>>

\begin{figure}[hb]
	\centering
	\includegraphics[width=\linewidth]{fig/showcase_3.png} 
	\caption{Showcase of dyngen functionality. \textbf{TODO: change to pdf.} Remove B?} % TODO: update label
	\label{fig:dyngen}
\end{figure}

@@

\begin{figure}[hb]
	\centering
	\includegraphics[width=\linewidth]{fig/simplecyclic_edited} 
	\caption{Showcase of dyngen functionality. A time resolution of 0.1 was used, but this can be increased or decreased without effect on performance of the execution of the simulation. \textbf{TODO: perhaps it's better to replace Figure \ref{fig:simplecyclic} with one subfigure for each of the paragraphs in this text.}}
	\label{fig:simplecyclic}
\end{figure}

@@

\section{Discussion}
As is, dyngen's single cell simulations can be used to evaluate common single-cell omics computational methods such as clustering, batch correction, trajectory inference and network inference.
However, the combined effect of these advantages results in a framework that is flexible enough to adapt to a broad range of applications, some of which may still be needed in the future. This may include methods that integrate clustering, network inference and trajectory inference. In this respect, dyngen may promote the development of new tools in the single-cell field similarly as other simulators have done in the past \textbf{10.1093/bioinformatics/btx631} \textbf{10.1093/bioinformatics/btr373} \textbf{10.1038/nmeth.3407}.

@@

Currently, dyngen focuses on simulating cells as standalone entities.
Future developments include extending the framework to simulate multiple cells in a virtual environment. Allowing cells to receive and react to environmental and intercellular stimuli would enable simulating essential cellular processes such as cell division and migration. 
%¡also adding more types of molecules, e.g. protein complex, small rnas, PPI
\section{Methods}
